MRD_final_microbiome

### 2019-06-26 import_popln_data.Rmd
updated

setwd("~/globalmicrobiome")
# files nwed to be in the owrking directory
mnd.incidence <- as.data.frame(read_csv("MND-I-B.csv",col_names = TRUE))
mnd.prev <- as.data.frame(read_csv("MND-P-B.csv",col_names = TRUE))
mnd.incidence <- mb.gather(mnd.incidence)
mnd.prev <- mb.gather(mnd.prev)

>>>>

setwd("~/globalmicrobiome")
# files nwed to be in the owrking directory

# For MND
mnd.incidence <- as.data.frame(read_csv("MND-I-B.csv",col_names = TRUE))
mnd.prev <- as.data.frame(read_csv("MND-P-B.csv",col_names = TRUE))

# Run function and change name
mnd.incidence <- mb.gather(mnd.incidence)
colnames(mnd.incidence)[2] <- "incidence"
mnd.prev <- mb.gather(mnd.prev)
colnames(mnd.prev)[2] <- "prevalance"

mnd.ip <- right_join(mnd.prev, mnd.incidence, by = "Location")

# For IPD
ipd.incidence <- as.data.frame(read_csv("PD-I-B.csv",col_names = TRUE))
ipd.prev <- as.data.frame(read_csv("PD-P-B.csv",col_names = TRUE))

# Run function and change name
ipd.incidence <- mb.gather(ipd.incidence)
colnames(ipd.incidence)[2] <- "incidence"
ipd.prev <- mb.gather(ipd.prev)
colnames(ipd.prev)[2] <- "prevalance"

ipd.ip <- right_join(ipd.prev, ipd.incidence, by = "Location")

# For AD
ad.incidence <- as.data.frame(read_csv("AD-I-B.csv",col_names = TRUE))
ad.prev <- as.data.frame(read_csv("AD-P-B.csv",col_names = TRUE))

# Run function and change name
ad.incidence <- mb.gather(ad.incidence)
colnames(ad.incidence)[2] <- "incidence"
ad.prev <- mb.gather(ad.prev)
colnames(ad.prev)[2] <- "prevalance"

ad.ip <- right_join(ad.prev, ad.incidence, by = "Location")
